A Data-Driven Framework for Neural Field Modeling

### 2011-07-21 ltx/first_order_framework/LaTeX_Manuscript.tex
editted xcorr analysis

\newcommand{\dean}[1]{\textcolor{red}{#1}}
\newcommand{\parham}[1]{\textcolor{blue}{#1}}
% \newcommand{\mike}[1]{\textcolor{Plum}{#1}}

@@

\bibliographystyle{./elsarticle/model2-names} 
\bibliography{BrainIDE}

@@

\clearpage
\newpage
\begin{table*}[!ht]
\begin{tabular}{|c|l|c|l|}
	\hline
	\textbf{Symbol} & \textbf{Quantity} & \textbf{Value} & \textbf{Units}\\
	\hline
	\multicolumn{4}{|c|}{\emph{Domain and indices}}\\
	\hline
	$\Delta$ & spatial discretization step & 0.5 & mm \\
	$T_s$ & time step & $0.001$ & s\\
	$T$ & number of time steps used in estimation & 400 & n.a.\\
	\hline 
\multicolumn{4}{|c|}{\emph{Model}}\\
	\hline
	$\tau$ & synaptic time constant & 0.01 & s$^{-1}$ \\
% 	$f_{max}$ & maximal firing rate & 10 & spikes.s$^{-1}$\\
	$\varsigma$ & slope of sigmoidal activation function & 0.56 \citep{Wendling2005} & mV$^{-1}$\\
	$v_0$ & firing threshold & 1.8 \citep{Marreiros2008} & mV  \\
	$\boldsymbol{\theta}$ & vector of connectivity kernel parameters & $\left[\begin{array}{ccc}
	100 &-80 &5
	\end{array}
	\right]^{\top}$ & mV.spike$^{-1}$\\
	$\sigma_{\psi_{1}}, \sigma_{\psi_{2}}, \sigma_{\psi_{3}}$ & connectivity kernel width parameters & 1.8, 2.4, 6 & mm\\
	$n_y$ & number of sensors & 196 & n.a.\\ 
	$\Delta_y$ & distance between adjacent sensors & 1.5 & mm\\
	$\sigma_{m}$ & observation kernel width parameter & 0.9 & mm \\
	$\Sigma_{\varepsilon}$ & observation noise variance & $0.1 \times I_{n_y}$ & mm$^2$ \\
	$\sigma_{\gamma}$& disturbance spatial covariance width & 1.3 & mm\\
	$\sigma_{d}$ & disturbance variance & 0.1 & mV \\
	\hline 
	\multicolumn{4}{|c|}{\emph{Reduced Model}}\\
	\hline
	$n_x$ & number of basis functions& 81 & n.a.\\
	$\Delta_{\phi}$ & distance between field basis functions & 2.5 & mm \\
	$\sigma_{\phi}$ & width of field basis functions in spatial domain & 1.58 & mm$^2$\\
	\hline 
	\multicolumn{4}{|c|}{\emph{Frequency Analysis}}\\
	\hline
	$\rho_y$ & sensor over-sampling parameter & 1 & n.a.\\
	$\rho_\phi$ & field basis function over-sampling parameter & 1.67 & n.a.\\
	\hline 
	\multicolumn{4}{|c|}{\emph{Estimation}}\\
	\hline
	$\alpha$& determines the spread of sigma points & 0.001 & n.a.\\
	$\beta$& prior knowledge of the sigma points distribution & 2 & n.a.\\
	$\kappa$& scaling parameter $(3-n_x)$& -78 & n.a.\\
	$\lambda$& scaling parameter & -80.99 & n.a.\\
	\hline
\end{tabular}
\caption{\textbf{Parameters.} Parameters for the neural field model, the reduced model, the frequency analysis and the estimation procedure.}
\label{tab:Parameters}
\end{table*}
\clearpage
\newpage
\begin{table*}[!ht]
\begin{tabular}{c|ccccc}
	Experiment & Parameter & Actual & Mean Est. & Std. Dev. & Bias (\%) \\ \hline

@@

% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig1.pdf} 
% \end{center}
% \caption{}
% \label{fig:Figure1}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig2.pdf} 
% \end{center}
% \caption{}
% \label{fig:Figure2}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig3.pdf}
% \end{center}
% \caption{} 
% \label{fig:Figure3}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig4.pdf}
% \end{center}
% \caption{}
% \label{fig:Figure4}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht] 
% \begin{center}
% \includegraphics{fig5.pdf}	
% \end{center}
% \caption{}
% \label{fig:Figure5}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig6.pdf}
% \end{center}
% \caption{}
% \label{fig:Figure6}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig7.pdf}
% \end{center}
% \caption{} 
% \label{fig:Figure7}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig8.pdf} 
% \end{center}
% \caption{} 
% \label{fig:Figure8}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig9.pdf}
% \end{center}
% \caption{}
% \label{fig:Figure9}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig10.pdf}
% \end{center}
% \caption{}
% \label{fig:Figure10}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig11.pdf}
% \end{center}
% \caption{}
% \label{fig:Figure11}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig12.pdf}
% \end{center}
% \caption{}
% \label{fig:Figure12}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig13.pdf}
% \end{center}
% \caption{}
% \label{fig:SensorAndSource}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig14.pdf}
% \end{center}
% \caption{}
% \label{fig:Ch3}
% \end{figure*}
\clearpage
\newpage
\appendix
\section{Time Discretization of the Neural Field Model}
\label{App:Time Discretization} This appendix provides a description of the discretization of the neural field model to form the integro-difference equation (IDE). To perform the discretization, we used a one-step Euler method, where equation~\ref{FinalFormContinuous} can be approximated by 
\begin{align}
	\label{Euler Approximation}\frac{v\left( \mathbf{r},t+T_s \right) - v\left( \mathbf{r},t\right)}{T_s} &=-\zeta v\left( \mathbf{r},t \right) \nonumber \\ 
&+ \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'}. 
\end{align}
For clarity, we shall index time points in the discrete time form of the model using the subscript $t$ and the next time point as $t+1$. Rearranging equation~\ref{Euler Approximation}, we get 
\begin{equation}
	\label{Euler Approximation2} v_{t+1}\left( \mathbf{r}\right) = v_t\left( \mathbf{r}\right) -T_s \zeta v_t\left( \mathbf{r}\right) + T_s \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'}. 
\end{equation}
Now making simplifications, the discrete time form of the model is 
\begin{equation}
	\label{Discrete Time Model1}v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'}, 
\end{equation}
where $\xi = 1 - T_s \zeta$.

>>>>

% \newcommand{\dean}[1]{\textcolor{red}{#1}}
% \newcommand{\parham}[1]{\textcolor{blue}{#1}}
% \newcommand{\mike}[1]{\textcolor{Plum}{#1}}

@@

\bibliographystyle{./elsarticle/model2-names} 
% \bibliographystyle{model2-names} 
\bibliography{BrainIDE}

@@

\clearpage
\newpage
\begin{table*}[!ht]
\begin{tabular}{|c|l|c|l|}
	\hline
	\textbf{Symbol} & \textbf{Quantity} & \textbf{Value} & \textbf{Units}\\
	\hline
	\multicolumn{4}{|c|}{\emph{Domain and indices}}\\
	\hline
	$\Delta$ & spatial discretisation step & 0.5 & mm \\
	$T_s$ & time step & $0.001$ & s\\
	$T$ & number of time steps used in estimation & 400 & n.a.\\
	\hline 
\multicolumn{4}{|c|}{\emph{Model}}\\
	\hline
	$\tau$ & synaptic time constant & 0.01 & s$^{-1}$ \\
% 	$f_{max}$ & maximal firing rate & 10 & spikes.s$^{-1}$\\
	$\varsigma$ & slope of sigmoidal activation function & 0.56 \citep{Wendling2005} & mV$^{-1}$\\
	$v_0$ & firing threshold & 1.8 \citep{Marreiros2008} & mV  \\
	$\boldsymbol{\theta}$ & vector of connectivity kernel parameters & $\left[\begin{array}{ccc}
	100 &-80 &5
	\end{array}
	\right]^{\top}$ & mV.spike$^{-1}$\\
	$\sigma_{\psi_{1}}, \sigma_{\psi_{2}}, \sigma_{\psi_{3}}$ & connectivity kernel width parameters & 1.8, 2.4, 6 & mm\\
	$n_y$ & number of sensors & 196 & n.a.\\ 
	$\Delta_y$ & distance between adjacent sensors & 1.5 & mm\\
	$\sigma_{m}$ & observation kernel width parameter & 0.9 & mm \\
	$\Sigma_{\varepsilon}$ & observation noise variance & $0.1 \times I_{n_y}$ & mm$^2$ \\
	$\sigma_{\gamma}$& disturbance spatial covariance width & 1.3 & mm\\
	$\sigma_{d}$ & disturbance variance & 0.1 & mV \\
	\hline 
	\multicolumn{4}{|c|}{\emph{Reduced Model}}\\
	\hline
	$n_x$ & number of basis functions& 81 & n.a.\\
	$\Delta_{\phi}$ & distance between field basis functions & 2.5 & mm \\
	$\sigma_{\phi}$ & width of field basis functions in spatial domain & 1.58 & mm$^2$\\
	\hline 
	\multicolumn{4}{|c|}{\emph{Frequency Analysis}}\\
	\hline
	$\rho_y$ & sensor over-sampling parameter & 1 & n.a.\\
	$\rho_\phi$ & field basis function over-sampling parameter & 1.67 & n.a.\\
	\hline 
	\multicolumn{4}{|c|}{\emph{Estimation}}\\
	\hline
	$\alpha$& determines the spread of sigma points & 0.001 & n.a.\\
	$\beta$& prior knowledge of the sigma points distribution & 2 & n.a.\\
	$\kappa$& scaling parameter $(3-n_x)$& -78 & n.a.\\
	$\lambda$& scaling parameter & -80.99 & n.a.\\
	\hline
\end{tabular}
\caption{\textbf{Parameters.} Parameters for the neural field model, the reduced model, the frequency analysis and the estimation procedure.}
\label{tab:Parameters}
\end{table*}
\clearpage
\newpage
\begin{table*}[!ht]
\begin{tabular}{c|ccccc}
	Experiment & Parameter & Actual & Mean Est. & Std. Dev. & Bias (\%) \\ \hline

@@

% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig1.pdf} 
% \end{center}
% \caption{}
% \label{fig:Figure1}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig2.pdf} 
% \end{center}
% \caption{}
% \label{fig:Figure2}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig3.pdf}
% \end{center}
% \caption{} 
% \label{fig:Figure3}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig4.pdf}
% \end{center}
% \caption{}
% \label{fig:Figure4}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht] 
% \begin{center}
% \includegraphics{fig5.pdf}	
% \end{center}
% \caption{}
% \label{fig:Figure5}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig6.pdf}
% \end{center}
% \caption{}
% \label{fig:Figure6}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig7.pdf}
% \end{center}
% \caption{} 
% \label{fig:Figure7}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig8.pdf} 
% \end{center}
% \caption{} 
% \label{fig:Figure8}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig9.pdf}
% \end{center}
% \caption{}
% \label{fig:Figure9}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig10.pdf}
% \end{center}
% \caption{}
% \label{fig:Figure10}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig11.pdf}
% \end{center}
% \caption{}
% \label{fig:Figure11}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig12.pdf}
% \end{center}
% \caption{}
% \label{fig:Figure12}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig13.pdf}
% \end{center}
% \caption{}
% \label{fig:SensorAndSource}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig14.pdf}
% \end{center}
% \caption{}
% \label{fig:Ch3}
% \end{figure*}

\clearpage
\newpage
\appendix
\section{Time Discretization of the Neural Field Model}
\label{App:Time Discretization} This appendix provides a description of the discretization of the neural field model to form the integro-difference equation (IDE). To perform the discretization, we used a one-step Euler method, where equation~\ref{FinalFormContinuous} can be approximated by 
\begin{align}
	\label{Euler Approximation}\frac{v\left( \mathbf{r},t+T_s \right) - v\left( \mathbf{r},t\right)}{T_s} &=-\zeta v\left( \mathbf{r},t \right) \nonumber \\ 
&+ \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'}. 
\end{align}
For clarity, we shall index time points in the discrete time form of the model using the subscript $t$ and the next time point as $t+1$. Rearranging equation~\ref{Euler Approximation}, we get 
\begin{equation}
	\label{Euler Approximation2} v_{t+1}\left( \mathbf{r}\right) = v_t\left( \mathbf{r}\right) -T_s \zeta v_t\left( \mathbf{r}\right) + T_s \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'}. 
\end{equation}
Now making simplifications, the discrete time form of the model is 
\begin{equation}
	\label{Discrete Time Model1}v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'}, 
\end{equation}
where $\xi = 1 - T_s \zeta$.
